\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-12-17 public/paper/pyg4ometry.tex
word order
elaborate on sphinx documentation

\section{Quality assurance}
The source and manual code for \PYGEOMETRY{} is stored in a Git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}),
where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx, a
Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages
available for Python as dependencies. \PYGEOMETRY{} has  two sub-packages
that require compilation: \pyinline{pyg4ometry.pycsg} in Python and
\pyinline{pyg4ometry.pycgal} in C++.
\PYGEOMETRY{} package dependencies and extensions are installed easily using
\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked
using software tests, of which there were 543 at the time of writing,
resulting in 84\% code coverage. The tests also serve as minimal examples to help users understand the code operation.

>>>>

\section{Quality assurance}
The source and manual code for \PYGEOMETRY{} is stored in a Git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}),
where a public issue tracker for users is hosted to report problems or bugs
with the code. The Python source is documented throughout using docstrings, which
are also used to generate an API reference using Sphinx, a
Python documentation generator
(\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}).  This
automatically-generated documentation is supplemented with
developer-written documentation in the form of examples and tutorials,
again using Sphinx. \PYGEOMETRY{} uses mature packages
available for Python as dependencies. \PYGEOMETRY{} has  two sub-packages
that require compilation: \pyinline{pyg4ometry.pycsg} in Python and
\pyinline{pyg4ometry.pycgal} in C++.
\PYGEOMETRY{} package dependencies and extensions are easily installed using
\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked
using software tests, of which there were 543 at the time of writing,
resulting in 84\% code coverage. The tests also serve as minimal examples to help users understand the code operation.
